The Weakly Nonlinear Saturation of the Magnetorotational Instability

### 2014-08-12 paper/mri paper.tex
a bit of multiscale discussion

>>>>

We conduct a formal multiscale analysis. Our perturbations are characterized in terms of fast and slow-moving variables, in order to simultaneously track their evolution on fast and slow scales. The relative scalings of the fast and slow scales are determined as follows. When our four equations are linearized for perturbations of the form $e^{\sigma t + i k_x x + i k_z z}$, we can derive the linear dispersion relation, which is fourth order in $\sigma$. The fast and slow variables are then defined such that each fluid quantity appears at the same lowest order in the linear dispersion relation.
